---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Anna Tschersich(Martrikelnummer), Name (Martrikelnummer), ..."
date: "`r Sys.Date()`"
output: distill::distill_article
---
```{r}
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
```


## Exercise 1: Initializing git 

### Exercise 1d:

**Strengths:**

a) Git is very fast, efficient and powerful.

b) Git is very helpful working together on a project by tracking all
changes in a project, aiding in teamwork and ensuring transparency.

**Weaknesses:**

a) For beginners, the functionality of git can be very challenging .

b) In very large teams, coordination becomes crucial to prevent loss of
work and conflicts when using Git. 



## Exercise 2: Putting your Repository on GitHub



## Exercise 3: Baby-Names in Munich 

### Exercise 3b:
```{r}
babynames_2022 <- read.csv("/Users/anna/2024-exeRcise-sheet-3/open_data_portal_2022.csv")
babynames_2023 <- read.csv("/Users/anna/2024-exeRcise-sheet-3/vornamen-muenchen-2023.csv")

typeof(babynames_2022$Anzahl) # Antwort: character
typeof(babynames_2023$Anzahl) # Antwort: character 

babynames_2022$Anzahl <- as.numeric(babynames_2022$Anzahl)
babynames_2023$Anzahl <- as.numeric(babynames_2023$Anzahl)

# R doesnt interpret the varibale "Anzahl" as numeric, as there are some values that are not just numbers but also text (e.g.: "4 oder weniger" as a value). 

# My solution is to change the types of the variable "Anzahl" in both datasets from character to numeric. Now the variable has the numerical datatype. Unfortunately all values that had text in it are now "NA" so the counts of some babynames got loss by changing the datatype. 
```

### Exercise 3c:
```{r}
sum(babynames_2022$Anzahl, na.rm = TRUE) #answer: 9899
sum(babynames_2023$Anzahl, na.rm = TRUE) #answer: 9277

# if we compare both numbers (ignoring the NA`s) we can assume that we had a bigger babyboom in 2022 as more babies were born in this year. 
```

### Exercise 3d:
```{r}
babynames_2022 <- babynames_2022 %>% mutate(year = 2022)
babynames_2023 <- babynames_2023 %>% mutate(year = 2023)
```

### Exercise 3e:
```{r}
combined_babynames <- bind_rows(babynames_2022, babynames_2023)
```

### Exercise 3f:
```{r}
popular_babynames <- combined_babynames %>%
  group_by(Vorname) %>%
  summarize(Anzahl_gesamt = sum(Anzahl, na.rm = TRUE)) %>%
  arrange(desc(Anzahl_gesamt))
```

```{r}
top_10_names <- head(popular_babynames, 10)
```

```{r}
table_top_babynames <- top_10_names %>%
  kbl(caption = "Top 10 Baby Names in Munich 2022/2023", label = "Table1") %>%
  kable_classic() %>%
  kable_styling(full_width = FALSE)

print(table_top_babynames)
```

## Exercise 4: Open Analysis 

### Exercise 4a: 
I chose the dataset "Number of deaths due to tetanus".

### Exercise 4c:
- Dataset Name: "Number of deaths due to tetanus"
- Link: https://github.com/owid/owid-datasets/blob/master/datasets/Number%20of%20deaths%20due%20to%20tetanus/Number%20of%20deaths%20due%20to%20tetanus.csv 

### Exercise 4d:

**Question:** Which year had the highest number of deaths due to tetanus?

I think answering this question is interesting and important to see how much medical progress has been made in tetanus research over the years. 

### Exercise 4e:
```{r}
deaths_tetanus <- read.csv("/Users/anna/2024-exeRcise-sheet-3/Number of deaths due to tetanus.csv")

deaths_tetanus <- deaths_tetanus %>%
group_by(Year) %>%
summarize(number_of_deaths_per_year = sum(Number.of.deaths.from.tetanus..GBD.2016.)) %>%
arrange(desc(number_of_deaths_per_year))

head(deaths_tetanus, n = 1) 

# answer to my chosen question: in 1990 the number of deaths due to tetanus were the highest (1332303	deaths)
```

### Exercise 4f:
```{r plot, fig.cap="the development of number of deaths due to tetanus over the years 1990 - 2016}
ggplot(
  data = deaths_tetanus,
  mapping = aes(
    x = Year,
    y = number_of_deaths_per_year
  )
) +
  geom_line() +
  labs(
    x = "Year (1990 - 2016)",
    y = "Number of deaths due to tetanus") +
  scale_y_continuous(trans = "log") +
  scale_x_continuous(breaks = seq(1990, 2016, by = 5)) 
```

**Short Interpretation:** 
As the plot, Figure\@ref(fig:plot), shows that the number of deaths due to tetanus constantly decreased over the years 1990 - 2016. 


